An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-17 paper.tex
added new frequency plots and code
1) Changed code to average a spectrogram over 20 seconds in the hamming
window.  Also interpolated all signals to the same sampling rate and
clipped out the sections that were not under the influence of
longitudinal perturbations
2) Changed "dusty purple" to "red" in each code and updated legend
3) Edited the text in the report to reflect the results in the new
graphs
4) Fonts are still strange when saving to pdf

To show the effects of the treadmill dynamics and give an idea of the frequency
content of the actual perturbations, the input and output for each speed were
transformed into the frequency domain using the Fast Fourier algorithm, and the
results are shown in Figure~\ref{fig:freq_analysis}. This shows that for the
1.2~\si{\meter\per\second} walking speed, the amplitude of the output is
significantly lower than the amplitude of the input signal at lower
frequencies. Additionally, the amplitude of output signal in the
0.8~\si{\meter\per\second} walking speed begins to attenuate around
2~\si{\hertz}, which is a noticeably lower frequency than the other walking
speeds.
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Frequency spectrum of the treadmill belt velocity input signal
    (purple) and the recorded output velocity (blue) for average belt speeds of
    0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:freq_analysis}
\end{figure}
\section*{Results}
\subsection*{Raw Data}
%
The raw data consists of a set of ASCII tab delimited text files output from
both the ``mocap'' and ``record'' modules in D-Flow in addition to a manually
generated YAML file that contains all of the necessary meta data for the given
trial. These three files are stored in a hierarchy of directories with one
trial per directory. The directories are named in the following fashion
\verb+T001/+ where \verb+T+ stands for ``trial'' and the following three digits
are provide a unique trial identification number.

>>>>

To show the effects of the treadmill dynamics and give an idea of the frequency
content of the actual perturbations, spectral analysis plots were created 
by averaging a spectrogram over twenty seconds in the hamming window, shown 
in Figure~\ref{fig:freq_analysis}. For all speeds, the frequency content of the
commanded and measured belt speeds were noticeably similar.  
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Frequency spectrum of the treadmill belt velocity input signal
    (purple) and the recorded output velocity (blue) for average belt speeds of
    0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:freq_analysis}
\end{figure}
\section*{Results}
\subsection*{Raw Data}
%
The raw data consists of a set of ASCII tab delimited text files output from
both the ``mocap'' and ``record'' modules in D-Flow in addition to a manually
generated YAML file that contains all of the necessary meta data for the given
trial. These three files are stored in a hierarchy of directories with one
trial per directory. The directories are named in the following fashion
\verb+T001/+ where \verb+T+ stands for ``trial'' and the following three digits
are provide a unique trial identification number.
